\section{Conclusions and Outlook}
\label{sec:conclusions}

This analysis note now presents a coherent GPR-based framework for the HPS narrow
prompt $A^\prime \rightarrow e^+e^-$ search in the language expected for internal
physics review. The physics target is stated explicitly in the minimal visible
dark-photon model, the HPS detector changes between the 2015/2016 baseline
configuration and the 2019/2021 upgraded configuration are documented explicitly, and
the signal-yield-to-$\eps^2$ conversion is tied directly to the dataset-specific
radiative-fraction inputs. The statistical workflow is likewise now more explicit: the
note distinguishes local bump-hunt significance from toy-tail limit diagnostics,
writes out the shared-$\eps^2$ likelihood used in the combined search, and makes the
role of the radiative-fraction penalty transparent both for individual datasets and
for the three-dataset combination.

The current physics-facing result is the systematic-penalized 2015$+$2016 10\%$+$2021
1\% shared-$\eps^2$ combination. That result already shows the central strengths of the
method: a smooth global GP background model, a leakage-retaining signal template, and a
coherent likelihood-level combination across statistically independent spectra with
different resolutions and normalizations. The updated note also makes clear which
pieces are mature and which remain auxiliary. In particular, the combined global
significance is the only look-elsewhere representation interpreted here, while the
single-dataset global overlays are retained only as bookkeeping for local fluctuation
context.

The refreshed two-dataset inputs sharpen that statistical interpretation. The updated
2015 and 2016 local-significance panels and the refreshed 2015$+$2016 combined suite
are all consistent with the bounded one-sided profile-likelihood convention: the local
$p_0$ curve never needs to exceed 0.5, while the dashed global overlay should be read
as a scan-level p-value or its clipped excess-significance representation. Within that
convention the two-dataset combined limit remains smooth, the 2016 panel still carries
the sharpest local structure, and none of those features yet warrant a frozen global
claim.

The remaining work is now well bounded. The batch3 refresh was sufficient to replace
the note-local 2015/2016 local-significance panels and the 2015$+$2016 combined suite,
but the current export tree still does not bundle the full standalone toy-tail tables or
the final scan-level max-$q_0$ calibration. The next frozen rerun should therefore
propagate the corrected plotting convention through a complete table bundle, regenerate
the \SI{119}{MeV} shared-signal display, and finalize the toy-based look-elsewhere
evaluation in the same production pass. With those updates in place, the framework
documented here is in a strong position to support the first fully combined HPS
GPR-based prompt-resonance result.
